The KMOS Deep Survey (KDS): dynamical measurements of $z\sim3.5$ main sequence galaxies\thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory. Programme IDs: }

### 2017-03-30 paper.tex
Finished all changes - about to send final draft to co-authors

\documentclass[fleqn,usenatbib]{mn2e}

\usepackage{hyperref}
\hypersetup{
  colorlinks,
  citecolor=blue,
  linkcolor=red,
  urlcolor=cyan}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
\usepackage{subcaption}
\usepackage{lscape}
\usepackage[LGRgreek]{mathastext}
\usepackage{enumitem}

@@

\author[O.J. Turner et al.]{
O. J. Turner,$^{1,2,\thanks{E-mail: turner@roe.ac.uk (OJT)}}$
M. Cirasuolo,$^{1,2}$
C. M. Harrison,$^{2,3}$
R. J. McLure,$^{1}$
J. S. Dunlop,$^{1}$\newauthor
A. M. Swinbank,$^{3,4}$
H. L. Johnson,$^{3,4}$
D. Sobral,$^{5}$
J. Matthee,$^{6}$
R. M. Sharples$^{3,4}$
\\
$^{1}$SUPA\thanks{Scottish Universities Physics Alliance}, Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh EH9 3HJ\\
$^{2}$European Southern Observatory, Karl-Schwarzschild-Str. 2, 85748 Garching b. M{\"u}nchen, Germany\\
$^{3}$Centre for Extragalactic Astronomy, Durham University, South Road, Durham, DH1 3LE, U.K.\\
$^{4}$Institute for Computational Cosmology, Durham University, South Road, Durham, DH1 3LE, U.K.\\
$^{5}$Department of Physics, Lancaster University, Lancaster, LA1 4BY, U.K.\\
$^{6}$Leiden Observatory, Leiden University, PO Box 9513, NL-2300 RA Leiden, the Netherlands}

@@

% Abstract of the paper
\begin{abstract}
We present dynamical measurements for 77 star-forming galaxies at $z\simeq3.5$ in the mass range $9.5 < log(M_{\star}/M_{\odot}) < 10.5$ from the KMOS ({\it K}-band Multi-Object Spectrograph) Deep Survey (KDS).
These measurements constrain the internal dynamics, the intrinsic velocity dispersions ($\sigma_{int}$) and rotation velocities ($V_{C}$) of galaxies in the high redshift Universe.
The mean velocity dispersion of the galaxies in our sample is $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$, consistent with the increase of $\sigma_{int}$ with redshift reported up to $z\simeq3$ in other samples, to which we have made careful comparisons.
However only $34 \pm 8\%$ of our galaxies are rotation-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much smaller than at lower redshift.
The rotation-dominated KDS galaxies show no clear offset from the local rotation velocity-stellar mass (i.e. $V_{C}-M_{\star}$) relation, although a smaller fraction of the galaxies are on the relation due to the increase in the dispersion-dominated fraction.
These observations are consistent with a simple equilibrium model picture, in which random motions are boosted in high redshift galaxies by the increase in gas fractions, accretion efficiency, specific star-formation rate and stellar feedback and may provide significant pressure support against gravity on the galactic disk scale.
\end{abstract}

@@

The picture is complicated by the addition of major and minor galaxy mergers which can rapidly change the physical properties of galaxies \citep[e.g.][]{Toomre1977,Lotz2008,Conselice2011,Conselice2014} and the relative importance of in-situ, secular stellar mass growth vs. stellar mass aggregation via mergers is the subject of much work involving both observations and simulations \citep[e.g.][]{Robaina2009,Kaviraj2012,Stott2013,Lofthouse2016,Qu2016}. 
To account for the growing number density of quiescent galaxies from z$\simeq2.5$ to the present day \citep[e.g.][]{Bell2004,Faber2007,Brown2007,Ilbert2010,Brammer2011,Muzzin2013,Buitrago2013} there must also be processes which shut off star-formation within main-sequence galaxies (i.e. quenching) which, to explain observations, must be a function of both mass and environment \citep{Peng2010,Darvish2016}.

Recent cosmological volume simulations provide subgrid recipes for the complex interplay of baryonic processes which are at work as galaxies evolve, and can track the development of individual galaxies from early stages, to maturity and through quenching \citep{Dubois2014a,Vogelsberger2014b,Schaye2015}.
Observations can aid the predictive power of such simulations by providing constraints on the evolving physical properties of galaxy populations.
The observed dynamical properties of galaxies contain information about the transfer of angular momentum between dark matter halos and the baryons and the dissipation of this angular momentum thereafter (through gravitational collapse, mergers and outflows e.g. \citealt{Fall1983,Romanowsky2012,Fall2013}), constituting an important set of quantities for simulations to reproduce.
Developments in both Integral-Field Spectroscopy (IFS) instrumentation and data analysis tools over the last decade have led to the observation of two-dimensional velocity and velocity dispersion fields for large samples of galaxies of different morphological types, spanning a wide redshift range \citep[e.g.][]{Sarzi2005,Flores2006,Epinat2008,ForsterSchreiber2009,Cappellari2011,Gnerucci2011,Epinat2012,Croom2012,Swinbank2012,Swinbank2012a,Bundy2015,Wisnioski2015,Stott2016,Harrison2017,Swinbank2017}.
When interpreted in tandem with high-resolution imaging data from the {\it Hubble Space Telescope (HST)}, these data provide information about the range of physical processes which are driving galaxy evolution.
In particular, in recent years the multiplexing capabilities of KMOS \citep{Sharples2013} have allowed for IFS kinematic observations for large galaxy samples to be assembled rapidly \citep{Sobral2013,Wisnioski2015,Stott2016,Mason2016,Harrison2017} providing an order-of-magnitude boost in statistical power over previous high redshift campaigns.

@@

There is also an increasing body of work measuring the relationship between the observed maximum rotation velocity of a galaxy, a tracer for the total dynamical mass, and its stellar mass, known as the stellar mass Tully-Fisher Relation (smTFR) \citep{Tully1977}, with surveys reporting disparate results for the evolution of this relation with redshift \citep[e.g.][]{Puech2008,Miller2011,Gnerucci2011,Swinbank2012,Simons2016,Tiley2016a,Harrison2017,Straatman2017,Ubler2017}.
Systematic differences in measurement and modelling techniques at high redshift, especially with regards to beam-smearing corrections, combine with our poor understanding of progenitors and descendants to blur the evolutionary picture which these surveys paint.
Additionally, there has been increasing focus in recent years on whether the measured velocity dispersions track random motions which provide partial gravitational support for high redshift galaxy disks \citep[e.g.][]{Burkert2010,Wuyts2016b,Ubler2017,Genzel2017,Lang2017}.
These random motions may become an increasingly significant component of the dynamical mass budget with increasing redshift \citep{Wuyts2016b} and pressure gradients across the disk could result in a decrease in the observed rotational velocities \citep{Burkert2010}. 
Different interpretations of the gaseous velocity dispersions and their role in providing pressure support against gravity also complicate the evolutionary picture. \\

@@

This paper focuses on the third question by deriving and interpreting the spatially-resolved kinematics of the KDS galaxies, particularly the rotation velocities and velocity dispersions, using the [O~{\sc III}]$\lambda$5007 emission line, discussing what we can learn about the nature of galaxy formation at $z\simeq3.5$ and forming evolutionary links with lower redshift work.
We seek also to minimise the impact of systematic differences introduced by the differing approaches in defining and extracting kinematic parameters when interpreting these trends.  
By making use of KMOS (with integration times of 7.5-9 hours) we have been able to study [O~{\sc III}]$\lambda$5007 emission in 77 galaxies spanning the mass range $9.5 < log(M_{\star}/M_{\odot}) < 10.5$, roughly tripling the number of galaxies observed via IFS at $z > 3$. \\

@@

\begin{figure*}
    \centering \hspace{-1.3cm}
    \begin{subfigure}[h!]{0.5\textwidth}
        \centering
        \includegraphics[height=3.5in]{rest_colour.png}
    \end{subfigure} \hspace{+0.4cm}
    \begin{subfigure}[h!]{0.5\textwidth}
        \centering
        \includegraphics[height=3.5in]{main_sequence.png}
    \end{subfigure}
    \caption{{\it Left:} The distribution of 49 KDS galaxies (see \cref{subsubsec:sed_fitting}) in rest-frame UVJ colour space is plotted, with filled symbols showing galaxies detected in [O~{\sc III}]$\lambda$5007 and open symbols showing those which were not detected.
    Also plotted in this plane are $\simeq4000$ galaxies in GOODS-S with $3.0 < z < 3.8$ (mirroring the KDS redshift range) from the 3D-{\em HST} survey  \protect\citep{Brammer2012,Momcheva2016}, with the filled squares denoting the density in of galaxies in that region.
    We use the galaxy selection criteria defined in \protect\cite{Whitaker2012a} to highlight star-forming and quiescent regions (motivated by the age sequence of quiescent galaxies), finding that the KDS galaxies are all clearly in the star-forming region and overlap with the highest density of 3D-{\em HST} targets.
    {\it Right:} We plot the location of the 49 KDS galaxies in the SFR versus M$_{\star}$ plane, using the same symbol convention. 
    The same GOODS-S galaxies from the 3D-{\em HST} survey as in the left panel are plotted with the filled squares as a reference for the typical relationship between SFR and $M_{\star}$.
    The black solid line and the dashed line show the $z\simeq2.5$ broken power-law and quadratic fit to the main-sequence respectively, described in \protect\cite{Whitaker2014}.
    We include the MS relation evaluated at $z=3.5$ (the median redshift of the KDS sample) described in \protect\cite{Speagle2014} and given in Equation \protect\ref{eq:speagle_ms} as the green line, with the discrepancy between the two relations representating the expected main-sequence evolution between these redshifts. 
    Within the typical uncertainties (see error bars) the KDS sample is representative of $z\simeq3.5$ SFGs.}
    \label{fig:main_sequence}
\end{figure*}

@@

\subsubsection{SED fitting and main-sequence}\label{subsubsec:sed_fitting}
In order to constrain their SFRs and stellar masses, the available photometry for the KDS targets was analysed using the SED fitting software described in \cite{McLure2011} and \cite{McLeod2015}.
The photometry for each target was fit with the same set of solar metallicity BC03 \citep{Bruzual2003} templates recommended for reproducing the properties of star-forming galaxies by \cite{Wuyts2011a}, and derived stellar masses and SFRs were based on a Chabrier IMF.
During the SED fitting process, dust attenuation was accounted for using the \cite{Calzetti2000} reddening law, with dust attenuation allowed to vary freely within the range $0.0<A_{V}<2.5$.
Based on the adopted template set, the median stellar mass for the full observed sample is $\log(M_{\star}/{\rm M}_{\odot}) = 10.0$. 
We note that fitting the photometry of the KDS targets with 0.2Z$\odot$ templates, rather than solar metallicity templates, typically reduces the derived stellar masses by $\simeq0.1$ dex, but this change does not affect the conclusions of this work.
In SSA22, 29 targets (36\% of the full KDS sample) do not have robust SFR measurements due to being undetected at $\geq 2\sigma$ significance in the available $J-$ and $K-$band photometry.
The median of the ratio of the derived stellar masses in GOODS-S to the matched stellar masses in \cite{Santini2015} (which presents an average result from 10 different sets of analyses) shows that the masses adopted here are $\simeq0.15$ dex larger. \\

In the left panel of Figure \ref{fig:main_sequence} we plot the 64\% of KDS galaxies with SFR measurements in the rest-frame {\it U-V} vs. {\it V-J} colour space.
This is a commonly used diagnostic plane for selecting star-forming and quiescent galaxies \citep[e.g.][]{Williams2009,Brammer2011,Whitaker2012a} with the age gradients of the stars within quiescent galaxies placing them in a different region of the plane to those which are actively forming stars.
The selection criteria defined in \cite{Whitaker2012a} (which evolve only gently with redshift) separate quiescent and star-forming regions, which are indicated by the black wedge.
We also make use of the rest-frame colours of $\simeq4000$ primarily star-forming galaxies located in GOODS-S between $3.0 < z < 3.8$ (based upon the `z\_best classification flag') from the 3D-{\em HST} survey \citep{Brammer2012,Momcheva2016}.
The filled squares indicate the density of 3D-{\em HST} targets in colour space and we observe that the peak density location is consistent with the location of the KDS targets, all of which are in the star-forming region.

@@

b012141\_012208 & 03:32:23.290 & $-$27:51:57.348 & 3.471        & 24.12  & 10.2 & 59 & 0.36        & 72        & 9     & 1.57      \\
b15573          & 03:32:27.638 & $-$27:50:59.676 & 3.583        & 23.6   & 10.4 & 27 & 0.28        & 78        & 146   & 0.52      \\
bs006516        & 03:32:14.791 & $-$27:50:46.500 & 3.215        & 23.94  & 9.9  & 14 & 0.50         & 61        & 146   & 1.91      \\
bs006541        & 03:32:14.820 & $-$27:52:04.620 & 3.475       & 23.44  & 10.2 & 18 & 0.44        & 66        & 168   & 1.83      \\
bs008543        & 03:32:17.890 & $-$27:50:50.136 & 3.474        & 22.73  & 10.7 & 42 & 0.50         & 61        & 67    & 1.59      \\
bs009818        & 03:32:19.810 & $-$27:53:00.852 & 3.706        & 24.18  & 9.8  & 33 & 0.80         & 37        & 148   & 1.24      \\
bs014828        & 03:32:26.760 & $-$27:52:25.896 & 3.562        & 23.58  & 10.2 & 30 & 0.31        & 76        & 63    & 1.61      \\
bs016759        & 03:32:29.141 & $-$27:48:52.596 & 3.602       & 23.85  & 10.0  & 9  & 0.65        & 50        & 49    & 0.87      \\
lbg\_20         & 03:32:41.244 & $-$27:52:20.676 & 3.225        & 24.97  & 9.6  & 5  & 0.64        & 52        & 1     & 1.28      \\
lbg\_24         & 03:32:39.754 & $-$27:39:56.628 & 3.279       & 24.67  & 9.7  & 6  & 0.53        & 60        & 34    & 1.27      \\
lbg\_25         & 03:32:29.189 & $-$27:40:22.476 & 3.322        & 24.95  & 9.4  & 6  & 0.30         & 76        & 78    & 1.18      \\
lbg\_30         & 03:32:42.854 & $-$27:42:06.300 & 3.419        & 23.85  & 10.1  & 29  & 0.79         & 38        & 66    & 0.95      \\
lbg\_32         & 03:32:34.399 & $-$27:41:24.324 & 3.417      & 23.84  & 10.2 & 52 & 0.60         & 54        & 40    & 1.88      \\
lbg\_38         & 03:32:22.474 & $-$27:44:38.436 & 3.488       & 24.58  & 10.0 & 8  & 0.58        & 56        & 137   & 0.92      \\

@@

lbg\_94         & 03:32:28.949 & $-$27:44:11.688 & 3.367       & 24.54  & 10.0 & 8  & 0.22        & 84        & 81    & 1.16      \\
lbg\_105        & 03:32:24.005 & $-$27:52:16.140 & 3.092      & 23.79  & 9.8  & 30 & 0.56        & 57        & 128   & 1.72      \\
lbg\_109        & 03:32:20.935 & $-$27:43:46.344 & 3.600       & 24.63  & 9.7  & 9  & 0.60         & 54        & 119   & 1.98      \\
lbg\_111        & 03:32:42.497 & $-$27:45:51.696 & 3.609       & 24.01  & 9.7  & 27 & 0.74        & 42        & 80    & 0.64      \\
lbg\_112         & 03:32:17.134 & $-$27:42:17.784 & 3.617        & 25.16  & 9.7  & 5  & 0.79         & 38        & 43    & 0.46      \\
lbg\_113        & 03:32:35.957 & $-$27:41:49.956 & 3.622      & 24.01  & 9.8  & 41 & 0.52        & 60        & 15    & 0.87      \\
lbg\_124         & 03:32:33.324 & $-$27:50:07.332 & 3.794        & 24.96  & 9.1  & 10  & 0.56         & 57        & 50    & 0.78      \\
$^{*}$n3\_006       & 22:17:24.859 & +00:11:17.620 & 3.069     & 22.98 & 10.6 & 50 & 0.57         & 57        & -    & 2.52      \\
n3\_009       & 22:17:28.330 & $+$00:12:11.600 & 3.069 & -    & 8.7  & -            & 0.75        & 42        & 84    & 1.06      \\
n\_c3         & 22:17:32.585 & $+$00:10:57.180 & 3.096       & 24.96 & 9.9  & -            & 0.71        & 46        & 94    & 0.56      \\
lab18         & 22:17:28.850 & $+$00:07:51.800 & 3.101           & -    & 8.7  & -            & 0.85        & 32        & 27    & 0.46      \\
$^{*}$lab25         & 22:17:22.603 & $+$00:15:51.330 & 3.067      & -    & 8.8  & -            & 0.57         & 57        & -    & 2.18      \\
s\_sa22a-d3   & 22:17:32.453 & $+$00:11:32.920 & 3.069 & 23.46 & 9.9  & -            & 0.39        & 70        & 125   & 1.78      \\
s\_sa22b-c20  & 22:17:48.845 & $+$00:10:13.840 & 3.196     & 23.91 & 9.7  & -            & 0.57        & 57        & 76    & 1.59      \\
$^{*}$s\_sa22b-d5  & 22:17:35.808 & $+$00:06:10.340 & 3.175 & 23.72 & 10.3 & -            & 0.57         & 57        & -    & 3.30      \\
s\_sa22b-d9   & 22:17:22.303 & $+$00:08:04.130 & 3.084    & 24.25 & 10.1 & -            & 0.65        & 50        & 60   & 0.5       \\
$^{*}$s\_sa22b-md25 & 22:17:41.690 & $+$00:06:20.460 & 3.304     & 24.62 & 9.1  & -            & 0.57         & 57        & -    & 1.39

>>>>

\documentclass[fleqn,usenatbib]{mnras}

\usepackage{hyperref}
\hypersetup{
  colorlinks,
  citecolor=blue,
  linkcolor=red,
  urlcolor=blue}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
\usepackage[compatibility=false]{caption}
\usepackage{subcaption}
\usepackage{lscape}
\usepackage[LGRgreek]{mathastext}
\usepackage{enumitem}

@@

\author[O.J. Turner et al.]{
O. J. Turner,$^{1,2,\thanks{E-mail: turner@roe.ac.uk (OJT)}}$
M. Cirasuolo,$^{1,2}$
C. M. Harrison,$^{2,3}$
R. J. McLure,$^{1}$
J. S. Dunlop,$^{1}$\newauthor
A. M. Swinbank,$^{3,4}$
H. L. Johnson,$^{3,4}$
D. Sobral,$^{5}$
J. Matthee,$^{6}$
R. M. Sharples$^{3,4}$
\\
$^{1}SUPA\thanks{Scottish Universities Physics Alliance}$, Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh EH9 3HJ\\
$^{2}$European Southern Observatory, Karl-Schwarzschild-Str. 2, 85748 Garching b. M{\"u}nchen, Germany\\
$^{3}$Centre for Extragalactic Astronomy, Durham University, South Road, Durham, DH1 3LE, U.K.\\
$^{4}$Institute for Computational Cosmology, Durham University, South Road, Durham, DH1 3LE, U.K.\\
$^{5}$Department of Physics, Lancaster University, Lancaster, LA1 4BY, U.K.\\
$^{6}$Leiden Observatory, Leiden University, PO Box 9513, NL-2300 RA Leiden, the Netherlands}

@@

% Abstract of the paper
\begin{abstract}
We present dynamical measurements for 77 star-forming galaxies at $z\simeq3.5$ in the mass range $9.0 < log(M_{\star}/M_{\odot}) < 10.5$ from the KMOS ({\it K}-band Multi-Object Spectrograph) Deep Survey (KDS).
These measurements constrain the internal dynamics, the intrinsic velocity dispersions ($\sigma_{int}$) and rotation velocities ($V_{C}$) of galaxies in the high redshift Universe.
The mean velocity dispersion of the galaxies in our sample is $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$, consistent with the increase of $\sigma_{int}$ with redshift reported up to $z\simeq3$ in other samples, to which we have made careful comparisons.
However only $34 \pm 8\%$ of our galaxies are rotation-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much smaller than at lower redshift.
The rotation-dominated KDS galaxies show no clear offset from the local rotation velocity-stellar mass (i.e. $V_{C}-M_{\star}$) relation, although a smaller fraction of the galaxies are on the relation due to the increase in the dispersion-dominated fraction.
These observations are consistent with a simple equilibrium model picture, in which random motions are boosted in high redshift galaxies by the increase in gas fractions, accretion efficiency, specific star-formation rate and stellar feedback and may provide significant pressure support against gravity on the galactic disk scale.
\end{abstract}

@@

The picture is complicated by the addition of major and minor galaxy mergers which can rapidly change the physical properties of galaxies \citep[e.g.][]{Toomre1977,Lotz2008,Conselice2011,Conselice2014} and the relative importance of in-situ, secular stellar mass growth vs. stellar mass aggregation via mergers is the subject of much work involving both observations and simulations \citep[e.g.][]{Robaina2009,Kaviraj2012,Stott2013,Lofthouse2017,Qu2017}. 
To account for the growing number density of quiescent galaxies from z$\simeq2.5$ to the present day \citep[e.g.][]{Bell2004,Faber2007,Brown2007,Ilbert2010,Brammer2011,Muzzin2013,Buitrago2013} there must also be processes which shut off star-formation within main-sequence galaxies (i.e. quenching) which, to explain observations, must be a function of both mass and environment \citep{Peng2010,Darvish2016}.

Recent cosmological volume simulations provide subgrid recipes for the complex interplay of baryonic processes which are at work as galaxies evolve, and can track the development of individual galaxies from early stages, to maturity and through quenching \citep{Dubois2014a,Vogelsberger2014b,Schaye2015}.
Observations can aid the predictive power of such simulations by providing constraints on the evolving physical properties of galaxy populations.
The observed dynamical properties of galaxies contain information about the transfer of angular momentum between dark matter halos and the baryons and the dissipation of this angular momentum thereafter (through gravitational collapse, mergers and outflows e.g. \citealt{Fall1983,Romanowsky2012,Fall2013}), constituting an important set of quantities for simulations to reproduce.
Developments in both Integral-Field Spectroscopy (IFS) instrumentation and data analysis tools over the last decade have led to the observation of two-dimensional velocity and velocity dispersion fields for large samples of galaxies of different morphological types, spanning a wide redshift range \citep[e.g.][]{Sarzi2005,Flores2006,Epinat2008,ForsterSchreiber2009,Cappellari2011,Gnerucci2011,Epinat2012,Croom2012,Swinbank2012,Swinbank2012a,Bundy2015,Wisnioski2015,Stott2016,Harrison2017,Swinbank2017}.
When interpreted in tandem with high-resolution imaging data from the {\it Hubble Space Telescope (HST)}, these data provide information about the range of physical processes which are driving galaxy evolution.
In particular, in recent years the multiplexing capabilities of KMOS \citep{Sharples2013} have allowed for IFS kinematic observations for large galaxy samples to be assembled rapidly \citep{Sobral2013,Wisnioski2015,Stott2016,Mason2017,Harrison2017} providing an order-of-magnitude boost in statistical power over previous high redshift campaigns.

@@

There is also an increasing body of work measuring the relationship between the observed maximum rotation velocity of a galaxy, a tracer for the total dynamical mass, and its stellar mass, known as the stellar mass Tully-Fisher Relation (smTFR) \citep{Tully1977}, with surveys reporting disparate results for the evolution of this relation with redshift \citep[e.g.][]{Puech2008,Miller2011,Gnerucci2011,Swinbank2012,Simons2016,Tiley2016,Harrison2017,Straatman2017,Ubler2017}.
Systematic differences in measurement and modelling techniques at high redshift, especially with regards to beam-smearing corrections, combine with our poor understanding of progenitors and descendants to blur the evolutionary picture which these surveys paint.
Additionally, there has been increasing focus in recent years on whether the measured velocity dispersions track random motions which provide partial gravitational support for high redshift galaxy disks \citep[e.g.][]{Burkert2010,Wuyts2016b,Ubler2017,Genzel2017,Lang2017}.
These random motions may become an increasingly significant component of the dynamical mass budget with increasing redshift \citep{Wuyts2016b} and pressure gradients across the disk could result in a decrease in the observed rotational velocities \citep{Burkert2010}. 
Different interpretations of the gaseous velocity dispersions and their role in providing pressure support against gravity also complicate the evolutionary picture. \\

@@

This paper focuses on the third question by deriving and interpreting the spatially-resolved kinematics of the KDS galaxies, particularly the rotation velocities and velocity dispersions, using the [O~{\sc III}]$\lambda$5007 emission line, discussing what we can learn about the nature of galaxy formation at $z\simeq3.5$ and forming evolutionary links with lower redshift work.
We seek also to minimise the impact of systematic differences introduced by the differing approaches in defining and extracting kinematic parameters when interpreting these trends.  
By making use of KMOS (with integration times of 7.5-9 hours) we have been able to study [O~{\sc III}]$\lambda$5007 emission in 77 galaxies spanning the mass range $9.0 < log(M_{\star}/M_{\odot}) < 10.5$, roughly tripling the number of galaxies observed via IFS at $z > 3$. \\

@@

\begin{figure*}
    \centering \hspace{-1.3cm}
    \begin{subfigure}[h!]{0.5\textwidth}
        \centering
        \includegraphics[height=3.5in]{rest_colour.png}
    \end{subfigure} \hspace{+0.4cm}
    \begin{subfigure}[h!]{0.5\textwidth}
        \centering
        \includegraphics[height=3.5in]{main_sequence.png}
    \end{subfigure}
    \caption{{\it Left:} The distribution of all 77 KDS galaxies in rest-frame UVJ colour space is plotted, with filled symbols showing galaxies detected in [O~{\sc III}]$\lambda$5007 and open symbols showing those which were not detected.
    Also plotted in this plane are $\simeq4000$ galaxies in GOODS-S with $3.0 < z < 3.8$ (mirroring the KDS redshift range) from the 3D-{\em HST} survey  \protect\citep{Brammer2012,Momcheva2016}, with the filled squares denoting the density in of galaxies in that region.
    We use the galaxy selection criteria defined in \protect\cite{Whitaker2012a} to highlight star-forming and quiescent regions (motivated by the age sequence of quiescent galaxies), finding that the KDS galaxies are all clearly in the star-forming region and overlap with the highest density of 3D-{\em HST} targets.
    {\it Right:} We plot the location of the KDS galaxies in the SFR versus M$_{\star}$ plane, using the same symbol convention. 
    The same GOODS-S galaxies from the 3D-{\em HST} survey as in the left panel are plotted with the filled squares as a reference for the typical relationship between SFR and $M_{\star}$.
    The black solid line and the dashed line show the $z\simeq2.5$ broken power-law and quadratic fit to the main-sequence respectively, described in \protect\cite{Whitaker2014}.
    We include the MS relation evaluated at $z=3.5$ (the median redshift of the KDS sample) described in \protect\cite{Speagle2014} and given in Equation \protect\ref{eq:speagle_ms} as the green line, with the discrepancy between the two relations representating the expected main-sequence evolution between these redshifts. 
    Within the typical uncertainties (see error bars) the KDS sample is representative of $z\simeq3.5$ SFGs.}
    \label{fig:main_sequence}
\end{figure*}

@@

\subsubsection{SED fitting and main-sequence}\label{subsubsec:sed_fitting}
In order to constrain their SFRs and stellar masses, the available photometry for the KDS targets was analysed using the SED fitting software described in \cite{McLure2011} and \cite{McLeod2015}.
The photometry for each target was fit with the same set of solar metallicity BC03 \citep{Bruzual2003} templates recommended for reproducing the properties of star-forming galaxies by \cite{Wuyts2011a}, and derived stellar masses and SFRs were based on a Chabrier IMF.
During the SED fitting process, dust attenuation was accounted for using the \cite{Calzetti2000} reddening law, with dust attenuation allowed to vary freely within the range $0.0<A_{V}<2.5$.
Based on the adopted template set, the median stellar mass for the full observed sample is $\log(M_{\star}/{\rm M}_{\odot}) = 9.8$. 
We note that fitting the photometry of the KDS targets with 0.2Z$\odot$ templates, rather than solar metallicity templates, typically reduces the derived stellar masses by $\simeq0.1$ dex, but this change does not affect the conclusions of this work.
In GOODS-S, we have compared our derived stellar masses to those in \cite{Santini2015} (which presents an average result from 10 different sets of analyses), finding a median difference between the two sets of values of $\Delta \log(M_{\star}/{\rm M}_{\odot}) = 9.8$ \\

In the left panel of Figure \ref{fig:main_sequence} we plot the KDS galaxies in the rest-frame {\it U-V} vs. {\it V-J} colour space.
This is a commonly used diagnostic plane for selecting star-forming and quiescent galaxies \citep[e.g.][]{Williams2009,Brammer2011,Whitaker2012a} with the age gradients of the stars within quiescent galaxies placing them in a different region of the plane to those which are actively forming stars.
The selection criteria defined in \cite{Whitaker2012a} (which evolve only gently with redshift) separate quiescent and star-forming regions, which are indicated by the black wedge.
We also make use of the rest-frame colours of $\simeq4000$ primarily star-forming galaxies located in GOODS-S between $3.0 < z < 3.8$ (based upon the `z\_best classification flag') from the 3D-{\em HST} survey \citep{Brammer2012,Momcheva2016}.
The filled squares indicate the density of 3D-{\em HST} targets in colour space and we observe that the peak density location is consistent with the location of the KDS targets, all but one of which are in the star-forming region.

@@

b012141\_012208 & 03:32:23.290 & $-$27:51:57.348 & 3.471        & 24.12  & 9.84 & 97 & 0.36        & 72        & 9     & 1.57      \\
b15573          & 03:32:27.638 & $-$27:50:59.676 & 3.583        & 23.6   & 9.76 & 172 & 0.28        & 78        & 146   & 0.52      \\
bs006516        & 03:32:14.791 & $-$27:50:46.500 & 3.215        & 23.94  & 9.75  & 14 & 0.50         & 61        & 146   & 1.91      \\
bs006541        & 03:32:14.820 & $-$27:52:04.620 & 3.475       & 23.44  & 10.1 & 10 & 0.44        & 66        & 168   & 1.83      \\
bs008543        & 03:32:17.890 & $-$27:50:50.136 & 3.474        & 22.73  & 10.5 & 20 & 0.50         & 61        & 67    & 1.59      \\
bs009818        & 03:32:19.810 & $-$27:53:00.852 & 3.706        & 24.18  & 9.7  & 33 & 0.80         & 37        & 148   & 1.24      \\
bs014828        & 03:32:26.760 & $-$27:52:25.896 & 3.562        & 23.58  & 9.7 & 92 & 0.31        & 76        & 63    & 1.61      \\
bs016759        & 03:32:29.141 & $-$27:48:52.596 & 3.602       & 23.85  & 9.9  & 6  & 0.65        & 50        & 49    & 0.87      \\
lbg\_20         & 03:32:41.244 & $-$27:52:20.676 & 3.225        & 24.97  & 9.5  & 5  & 0.64        & 52        & 1     & 1.28      \\
lbg\_24         & 03:32:39.754 & $-$27:39:56.628 & 3.279       & 24.67  & 9.6  & 5  & 0.53        & 60        & 34    & 1.27      \\
lbg\_25         & 03:32:29.189 & $-$27:40:22.476 & 3.322        & 24.95  & 9.4  & 5  & 0.30         & 76        & 78    & 1.18      \\
lbg\_30         & 03:32:42.854 & $-$27:42:06.300 & 3.419        & 23.85  & 10.0  & 18  & 0.79         & 38        & 66    & 0.95      \\
lbg\_32         & 03:32:34.399 & $-$27:41:24.324 & 3.417      & 23.84  & 9.9 & 64 & 0.60         & 54        & 40    & 1.88      \\
lbg\_38         & 03:32:22.474 & $-$27:44:38.436 & 3.488       & 24.58  & 9.9 & 5  & 0.58        & 56        & 137   & 0.92      \\

@@

lbg\_94         & 03:32:28.949 & $-$27:44:11.688 & 3.367       & 24.54  & 9.9 & 8  & 0.22        & 84        & 81    & 1.16      \\
lbg\_105        & 03:32:24.005 & $-$27:52:16.140 & 3.092      & 23.79  & 9.3  & 54 & 0.56        & 57        & 128   & 1.72      \\
lbg\_109        & 03:32:20.935 & $-$27:43:46.344 & 3.600       & 24.63  & 9.7  & 8  & 0.60         & 54        & 119   & 1.98      \\
lbg\_111        & 03:32:42.497 & $-$27:45:51.696 & 3.609       & 24.01  & 9.7  & 18 & 0.74        & 42        & 80    & 0.64      \\
lbg\_112         & 03:32:17.134 & $-$27:42:17.784 & 3.617        & 25.16  & 9.6  & 6  & 0.79         & 38        & 43    & 0.46      \\
lbg\_113        & 03:32:35.957 & $-$27:41:49.956 & 3.622      & 24.01  & 9.6  & 56 & 0.52        & 60        & 15    & 0.87      \\
lbg\_124         & 03:32:33.324 & $-$27:50:07.332 & 3.794        & 24.96  & 9.0  & 13  & 0.56         & 57        & 50    & 0.78      \\
$^{*}$n3\_006       & 22:17:24.859 & +00:11:17.620 & 3.069     & 22.98 & 10.5 & 14 & 0.57         & 57        & -    & 2.52      \\
n3\_009       & 22:17:28.330 & $+$00:12:11.600 & 3.069 & -    & 8.7  & 3            & 0.75        & 42        & 84    & 1.06      \\
n\_c3         & 22:17:32.585 & $+$00:10:57.180 & 3.096       & 24.96 & 9.8  & 4            & 0.71        & 46        & 94    & 0.56      \\
lab18         & 22:17:28.850 & $+$00:07:51.800 & 3.101           & -    & 8.2  & 4            & 0.85        & 32        & 27    & 0.46      \\
$^{*}$lab25         & 22:17:22.603 & $+$00:15:51.330 & 3.067      & -    & 8.4  & 7            & 0.57         & 57        & -    & 2.18      \\
s\_sa22a-d3   & 22:17:32.453 & $+$00:11:32.920 & 3.069 & 23.46 & 9.7  & 60            & 0.39        & 70        & 125   & 1.78      \\
s\_sa22b-c20  & 22:17:48.845 & $+$00:10:13.840 & 3.196     & 23.91 & 9.5  & 45            & 0.57        & 57        & 76    & 1.59      \\
$^{*}$s\_sa22b-d5  & 22:17:35.808 & $+$00:06:10.340 & 3.175 & 23.72 & 10.2 & 9            & 0.57         & 57        & -    & 3.30      \\
s\_sa22b-d9   & 22:17:22.303 & $+$00:08:04.130 & 3.084    & 24.25 & 10.1 & 5            & 0.65        & 50        & 60   & 0.5       \\
$^{*}$s\_sa22b-md25 & 22:17:41.690 & $+$00:06:20.460 & 3.304     & 24.62 & 8.6  & 10            & 0.57         & 57        & -    & 1.39
